\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{titlesec, titling}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}

% Formatting
\titleformat{\section}{\large\bfseries\color{black}}{}{0em}{}[\titlerule]
\renewcommand{\labelitemi}{\textbullet}
\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt} % Üst çizgiyi kaldırır
\renewcommand{\footrulewidth}{0pt} % Alt çizgiyi kaldırır
\fancyhf{}
\rfoot{\thepage/\pageref{LastPage}}

\begin{document}

% Name and Title
\begin{center}
    {\LARGE \bfseries Yunus YILDIZ} \\
    {\large Full-Stack Developer} \\
    {\small Geneva, Switzerland}
\end{center}

% Contact Information

\noindent\textbf{Email:} \href{mailto:yunusyildiz@swissmail.com}{yunusyildiz@swissmail.com} \hfill
\textbf{Website:} \href{https://yunusyildiz.ch}{yunusyildiz.ch} \\
\textbf{LinkedIn:} \href{https://www.linkedin.com/in/yunusyildiz-ch/}{linkedin.com/in/yunusyildiz-ch} \hfill
\textbf{GitHub:} \href{https://github.com/yunusyildiz-ch}{github.com/yunusyildiz-ch}

\section*{Profile Summary}
\noindent A dedicated and ambitious \textbf{Full Stack Developer} with a strong foundation in front-end and back-end technologies. I see coding not just as a technical process but as a creative way to solve real-world challenges. Proficient in \textbf{JavaScript, React, Node.js, Express.js, HTML, CSS, and Bootstrap}, I have built various projects and am currently expanding my backend expertise by learning \textbf{Java}, with plans to deepen my knowledge in \textbf{Spring Boot and Angular}.  

\noindent One of my key projects, \textbf{SmartFox Home}, is a smart home management system that focuses on \textbf{heat optimization, energy efficiency, and user comfort}. This project has allowed me to work extensively on \textbf{IoT device integration, performance optimization, and user-friendly UI/UX development}. I strongly believe in leveraging technology to create sustainable and practical solutions that improve daily life.  

\noindent Having completed two intensive training programs at \textbf{HiCoders}, earning \textbf{Certificates of Excellence}, I have honed my ability to build scalable applications while continuously improving my skills. Adaptable and team-oriented, I thrive in dynamic environments where I can contribute my \textbf{analytical thinking, problem-solving abilities, and fast-learning mindset} to innovative projects.  

\noindent Additionally, I am currently enhancing my \textbf{French language proficiency} to integrate more effectively into international work environments. Excited to collaborate on impactful projects, develop scalable solutions, and grow as a developer within a forward-thinking team.  

\section*{Core Skills}
\begin{itemize}
    \item \textbf{Front-End:} HTML5, CSS3/Bootstrap, JavaScript, React, Tailwind CSS, Material-UI
    \item \textbf{Back-End:} Node.js, Express, REST APIs, MySQL
    \item \textbf{Version Control:} Git/GitHub
    \item \textbf{Additional:} Basic Arduino integration, CLI Basics, Problem-Solving, Communication
\end{itemize}

\section*{Education \ \& Certifications}
\begin{itemize}
    \item \textbf{Full Stack Web Programming Certificate of Excellence (2023–2024)} - HiCoders
    \item \textbf{Web Programming Basics Certificate of Excellence (2023)} - HiCoders
    \item \textbf{Bachelor’s in Psychological Counseling and Guidance (2009)} - Gazi University, Turkey
    \item \textbf{Bachelor’s in Political Science and Public Administration (2021)} - Anadolu University, Turkey
    \item \textbf{Associate’s in Law} - Atatürk University, Turkey
    \item \textbf{Turkish Military Academy (2010)} -  Turkey
\end{itemize}

\newpage

\section*{Project Experience}
\textbf{School Management System (Front-End \& Back-End)}
\begin{itemize}
    \item Developed a dynamic front-end with JavaScript, improving user experience.
    \item Created a robust RESTful API-based back-end for data handling.
\end{itemize}
\textbf{Heating System Optimization (Full Stack \& Arduino Integration)}
\begin{itemize}
    \item Implemented front-end and back-end solutions to manage heating systems.
    \item Integrated Arduino for enhanced data collection and system control.
\end{itemize}

\section*{Professional Experience}
\textbf{Psychological Counselor (2010) - Ministry of National Education, Turkey}
\begin{itemize}
    \item Provided guidance and counseling services, demonstrating strong communication skills.
\end{itemize}
\textbf{Military Officer (2010–2016) - Turkish Armed Forces}
\begin{itemize}
    \item Managed teams, operations, and strategic tasks, developing leadership abilities.
\end{itemize}
\textbf{Sales Representative (2022) - Betasan Medical Industry, Turkey}
\begin{itemize}
    \item Engaged with clients, improved negotiation skills, and supported product sales.
\end{itemize}

\section*{Additional Information}
\begin{itemize}
    \item Committed to continuous learning and professional growth.
    \item Actively expanding professional network to increase visibility in the Swiss job market.
    \item Enthusiastic about tackling complex challenges and delivering innovative solutions.
\end{itemize}

\section*{Hobbies}
Chess | Poetry | Hiking | Cycling | Cooking | Running | Coding

\end{document}
